---
title: "Code Book"
output: html_document
---

run_analysis.R uses the UCI HAR dataset provided at: 
https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip

A full description of the data set can be found here:
http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones

The columns are renamed in the following format: "descDIREC.quant", where desc is something like "tBodyAcc" or "fBodyGyro". Direc is X, Y, Z, or mag. quant is mean or std. This produces the following:

```{r, echo=FALSE}
names=read.table("~/tiny_data.txt")
subject=names[,1]
names=names[,-1]
activity=names[,1]
names=names[-1]
```

```{r}
names=colnames(names)
names
```

The subjects are integers, 1-30. The activity_labels are

```{r}
levels(activity)
```

Before pruning but after merging the train and test data, X is a 10299x561 data frame. After selecting out the mean and std data, it is a 10299x66 data frame. Including subject and activity_label columns, it is a 10299x68 data frame, and stored as cleaned_data.txt. After it is reduced to just means of each combination of subject and activity_label, it is a 180x68 data frame, and outputted to tiny_data.txt.
